\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-01-30 doc/publications/plos16/plos16.tex
fixed a couple of references

\cite{Bau.2012} provides a proof that a random forest model will converge at a rate that depends on
the cardinality of the set $S$ of ``strong predictors'' rather than on the number of variables $p$. That is, given a
function $y=f(S)$ depending on a set of variables $S$, a random forest will converge to the true function $y$ with a
rate that depends on the size of $S$ and not the number of noise variables in the data set. If the size of $S$ is small
compared to the total number of variables, then the rate of convergence will be quicker. It is not clear what the size
of the set $S$ will be in a GWAs application. There are cases of small groups of SNPs with large effects and also of
conditions caused by the interaction of large groups of SNPs.

@@

We also frequently see highly-ranked variants in chromosome 22q11. \cite{Stagi.2010}, observe that individuals with a
microdeletion in this region have a significant in bone mass\cite{Stagi2010}. In this same region, we also observe
variants present in PRODH (proline dehydrogenase). PRODH catalyzes the first step in proline degradation, and as
proposed by \cite{Phang.2008}, proline is made available by collagen degradation \cite{Phang2008}.

>>>>

\cite{Biau.2012} provides a proof that a random forest model will converge at a rate that depends on
the cardinality of the set $S$ of ``strong predictors'' rather than on the number of variables $p$. That is, given a
function $y=f(S)$ depending on a set of variables $S$, a random forest will converge to the true function $y$ with a
rate that depends on the size of $S$ and not the number of noise variables in the data set. If the size of $S$ is small
compared to the total number of variables, then the rate of convergence will be quicker. It is not clear what the size
of the set $S$ will be in a GWAs application. There are cases of small groups of SNPs with large effects and also of
conditions caused by the interaction of large groups of SNPs.

@@

We also frequently see highly-ranked variants in chromosome 22q11. \cite{Stagi.2010}, observe that individuals with a
microdeletion in this region have a significant in bone mass \cite{Stagi.2010}. In this same region, we also observe
variants present in PRODH (proline dehydrogenase). PRODH catalyzes the first step in proline degradation, and as
proposed by \cite{Phang.2008}, proline is made available by collagen degradation \cite{Phang.2008}.
